%-------------------------
% Resume in Latex
% Author : Alex Blackwell
%------------------------

\documentclass[letterpaper, 11pt]{article}
\usepackage{fontawesome}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fancyhdr}

\pdfinfo{
    /Author (Alex Blackwell)
    /Title (Alex Blackwell Resume)
}

\pagestyle{fancy}
\fancyhf{}  % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{0pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \small{
    \textbf{#1}{: #2 \vspace{5pt}} \\
  }
}

\newcommand{\project}[2]{
  \item\small{
    \href{#2}{\underline{#1}\hspace{3pt}(code link)}\textbf{:} \vspace{-5pt}
  }
  \begin{itemize}
}

\newcommand{\infoSection}[3]{
  \vspace{0pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {#2} \\
      {\small#3} \\
    \end{tabular*}\vspace{0pt}
    \begin{itemize}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeWorkExperience}[6]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2\\
      #3 \\
    \end{tabular*}\vspace{0pt}
    \begin{itemize}
        \item #4
        \item #5
        \item #6
    \end{itemize}
}

\newcommand{\resumeWorkExperienceLight}[5]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 \\
    \end{tabular*}\vspace{0pt}
    \begin{itemize}
        \item #4
        \item #5
    \end{itemize}
}

\newcommand{\resumeSubheading}[1]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\projectEnd}{\end{itemize}}
\newcommand{\infoSectionEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\huge Alex Blackwell} & Email: \href{mailto:alex_blackwell@sfu.ca}{alex\_blackwell@sfu.ca}\\
  \href{https://alexblackwell.ca/} {\faHome \hspace{0.1cm} alexblackwell.ca}
  & Phone: 604-767-4611 \\
  \href{https://github.com/Alex0Blackwell}{\faGithub \hspace{0.1cm} GitHub (github.com/alex0blackwell)} 
  & Vancouver, B.C. Canada \\
  \href{https://www.linkedin.com/in/alex-blackwell/}{\faLinkedin \hspace{0.1cm} LinkedIn (linkedin.com/in/alex-blackwell)}
  & Page 1

\end{tabular*}

%--------TECHNICAL-SKILLS------------
\section{Technical Skills}
    \resumeItem{Languages}
	{C++, Python, JavaScript, C}
    \resumeItem{Technologies}
	{HTML/CSS, Git, Unix command line, jQuery, Node.js, Continuous Integration, Jest Testing framework}
	\resumeItem {Applications}
	{GitHub, GitLab, Unity, Adobe Suite, Microsoft Office Suite, VIM, \LaTeX, WordPress, Jekyll}
    \resumeItem{Operating Systems}
	{GNU/Linux (Manjaro, Ubuntu, Kali), Windows, MacOS}
\vspace{-5pt}

%-----------PERSONAL-PROJECTS---------------
\section{Personal Projects}
    \resumeSubheading
      {Python Projects:}
      \resumeItemListStart
        \project{Desktop Application -- “Copy Paste Anything"} {https://github.com/Alex0Blackwell/copy-paste-anything}
          \item{Developed a desktop application to extract all text from any selected area of the screen.}
          \item{Utilized machine learning character recognition algorithms to accurately determine selected
          text.}
          \item{Implemented cross-platform algorithm to automatically save selected text to the clipboard to improve usability.}
          \item{Developed a Graphical User Interface to easily select any portion of the screen with a mouse cursor to improve user experience.}
        \projectEnd
        \project{Terminal command -- “Tree"} {https://github.com/Alex0Blackwell/tree}
          \item{Developed terminal command to display the file structure from the current working directory.}
          \item{Created algorithm to determine the most common file type utilizing the efficient look up times of a hashmap.}
          \item{Engineered recursive algorithm for traversing the file structure resulting in simplified and readable code.}
        \projectEnd
      \resumeItemListEnd
      \vspace{10pt}

    \resumeSubheading
      {JavaScript Projects:}
      \resumeItemListStart
        \project{Website -- “Merge Sort Visualizer"} {https://github.com/Alex0Blackwell/merge-sort-visualizer}
          \item{Programmed website capable of visually representing the process of a merge sort algorithm.}
          \item{Used Bootstrap to create a responsive and scalable website to work visually on all devices.}
          \item{Implemented asynchronous JavaScript code to add timing events without decreasing the responsiveness of the website.}
        \projectEnd
        \project{Browser Extension -- “QR-Code Generator"} {https://github.com/Alex0Blackwell/qr-code-extension}
          \item{Worked in a team to develop a browser extension during the twelve hour Hack-a-thon: System Hacks 2020.}
          \item{Responsible for converting text to a QR-code that is capable of representing a paragraph.}
          \item{Worked on both Chrome and Firefox to deploy the extension to become a product.}
        \projectEnd
      \resumeItemListEnd
      \vspace{10pt}

    \resumeSubheading
      {C++ Projects:}
      \resumeItemListStart
        \project{Terminal Application -- “CSS Minifier"} {https://github.com/Alex0Blackwell/css-minify}
          \item{Developed an algorithm to produce CSS with a lesser file size, reducing website load times and bandwidth usage.}
          \item{Designed the algorithm to allow for all valid styles of CSS formatting to improve usability for all developers.}
        \projectEnd
        \project{Data Structures} {https://github.com/Alex0Blackwell/c-cpp-DSA}
          \item{Implemented data structures to help understand the abstractions of common data structures.}
          \item{Implemented: binary search tree, singly linked list, queue, red black binary tree, stack, double ended queue, and binary heap.}
        \projectEnd
      \resumeItemListEnd

%------TECHNICAL-WORK-EXPERIENCE-----
\section{Technical Work Experience}
    \resumeWorkExperience
	{Freelance Website Developer} {May to September 2020} {Fiverr, Remote}
	{Worked with clients to develop professional websites which started companies and built online presence.}
	{Delivered high quality products to clients ahead of schedule, earning an overall rating of five stars.}
	{Used Bootstrap, JavaScript, HTML/CSS, Git, WordPress and Jekyll to create and improve professional websites.}

\newpage

%----------SECOND-PAGE-HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\huge Alex Blackwell} & Email: \href{mailto:alex_blackwell@sfu.ca}{alex\_blackwell@sfu.ca}\\
  \href{https://alexblackwell.ca/} {\faHome \hspace{0.1cm} alexblackwell.ca}
  & Phone: 604-767-4611 \\
  \href{https://github.com/Alex0Blackwell}{\faGithub \hspace{0.1cm} GitHub (github.com/alex0blackwell)} 
  & Vancouver, B.C. Canada \\
  \href{https://www.linkedin.com/in/alex-blackwell/}{\faLinkedin \hspace{0.1cm} LinkedIn (linkedin.com/in/alex-blackwell)}
  & Page 2

\end{tabular*}

%------OTHER-WORK-EXPERIENCE-----
\section{Other Work Experience}
    \resumeWorkExperienceLight
	{Skate Instructor} {September to May of 2016 -- 2019}
	{North Vancouver Recreation Commission, North Vancouver, B.C.}
	{Responsible for teaching children a new skill by clearly communicating and adapting to areas of struggle.}
	{Created a schedule for groups requiring time management for teaching classes.}
	\vspace{10pt}
	
    \resumeWorkExperienceLight
	{Park Ambassador} {May to September of 2016 -- 2019}
	{Capilano Suspension Bridge Park, North Vancouver, B.C.}
	{Accountable member of a team that interacted with guests to improve customer experience.}
	{Responsible for calming upset or unnerved guests at the park and providing solutions to their problems.}


%------EXTRA-CURRICULAR-ACTIVITIES-----
\section{Extra Curricular Activities}
    \infoSection
    {Simon Fraser Competitive Programming Club} {September 2020 -- Present}
    {Simon Fraser University, Burnaby, B.C.}
      \item Program in weekly competitions to improve competitive programming skills.
      \item Compete against computing science students to improve the speed and efficiency of solving problems.
      \item Study weekly lectures on algorithms and data structures to learn new methods and improve old methods of solving problems.
    \infoSectionEnd
    \vspace{10pt}
    \infoSection
    {Simon Fraser Hacking and Cybersecurity Club} {September 2019 -- Present}
    {Simon Fraser University, Burnaby, B.C.}
      \item Using a Kali Linux virtual machine to take advantage of cybersecurity tools native to the operating system.
      \item Utilized the Metasploit penetration testing framework to identify vulnerabilities.
      \item Tested Metasploit commands on the vulnerable virtual machine Metasploitable to ethically learn penetration testing.
    \infoSectionEnd


%-----------EDUCATION--------------
\section{Education}
    \resumeEducationHeading
      {Simon Fraser University}{Burnaby, B.C. Canada}
      {Computing Science;  GPA: 3.73}{September 2019 -- Present}

%-------HONOURS-AND-AWARDS---------
\section{Honours and Awards}
    \resumeItem{Dean's Honour Roll}
	{Simon Fraser University, Faculty of Applied Sciences, Spring 2020}
    \resumeItem{Simon Fraser University Open Scholarship}
	{Scholarship for academic achievement, Spring 2020}
    \resumeItem{Second place in Simon Fraser Coding Competition}
	{Hosted by S.F.U. competitive programming club, 02/09/2020}
    \resumeItem{Google Kickstart Top 35 in Canada}
	{Google Kickstart Coding Competition, 22/08/2020}

%-----------INTERESTS------------
\section{Interests}
    \resumeItem{Open source software development}
    {Enjoy contributing to software on GitHub and creating new projects.}
    \resumeItem{Image recognition machine learning}
    {Amateur photographer and enjoy seeing the combination of two interests.}
    \resumeItem{GNU/Linux operating systems}
    {Spend time trying new operating systems and creating new desktop environments.}

\end{document}

